Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-09-04 doc/paper.tex
update

     \subsection{Beam Search (BS)}
        BS is an incomplete BFS heuristic search algorithm.

>>>>

     \subsection{Beam Search (BS)}
        Beam Searxh is an incomplete BFS heuristic search algorithm. At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$. all nodes are then expanded in all possible ways. Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level. 
        The search is processed in the same manner until $B$ is empty. The main question concerns of the criterion of choosing the nodes for a beam. This is done by means of a heuristic evaluation of the nodes. The heuristic is a problem-specific aspect of each problem that has to be solved. \fxnote{work in progress...}
